---
title: "Analyze Form Responses"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Loading packages and reading data

First, we'll load two packages that we will use. These add particular functionality
to R.

```{r}
library(tidyverse)
library(janitor)
library(lubridate)
```

We'll read data from a URL. Note that the data is *anonymized* and was "published" via
Google Sheets:

```{r}
form_data <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vQWUfMMUboX4YMwz97zz_Z-lh2NrBbMbxVOf56LQooDHtdepLh-_-yXKOLOGHNdRmZI2Xn2kUVtstHH/pub?output=csv")
```

# Preparing data

## Renaming variables

Let's rename the variables to be easier to use.

Before that, let's clean them:

```{r}
form_data <- clean_names(form_data)

names(form_data)
```

They are still very long; however, now, we can more easily rename them:

```{r}
form_data <- form_data %>% 
  rename(prior_exp = what_is_the_extent_of_your_prior_experience_using_r_markdown,
         why_interest = why_in_brief_are_you_interested_in_learning_r_markdown_or_r,
         utk_affiliated = are_you_affiliated_with_the_university_of_tennessee_knoxville_as_a_student_or_faculty_staff_member,
         comments = do_you_have_any_other_questions_or_comments)
```

## Modifying variables

One variables need some additional processing to be more useful to us, `timestamp`.

We'll start with `timestamp`, which needs to be recognized as a time:

```{r}
form_data <- form_data %>% 
  mutate(timestamp = mdy_hms(timestamp))
```

Let's check that it worked:

```{r}
form_data
```

# Try it out!

## Count them up!

Now, it's your turn to try it out.

First, try to determine how many respondents were UTK affiliated, using the `count()` 
function. To use this, you have to include the name of the variable that you want
to count between the open and close parentheses just following the word "count".

You don't need to quote the variable - you replace ??? with its name, and then 
click run (the green arrow to the far right of the chunk).

```{r}
form_data %>% 
  count(???)
```

## Filter

Imagine we wanted to filter the data to only include those with prior experience 
at the value of 4 or lower. We can use the `filter()` function to do this.

Filter requires a *logical condition* created by a *logical operator*, such as 
the following:

```{r, eval = FALSE}
==
>
<
>=
<=
```

Which logical operator can you use to only include those with prior experience 
at the value of 4 or lower? Replace ??? below and then click run to see the 
result.

```{r}
form_data %>% 
  filter(prior_exp ???)
```

##

Last, imagine that we wish to plot the distribution of prior experience. We 
can use the ggplot2 package to do this, replacing the ??? with the name of 
the variable you want to plot

```{r}
ggplot(form_data, 
       aes(x = ???)) +
  geom_histogram()
```

# Extensions

Made it through he above? Try a few extensions. Here are a few ideas:

- Plot the number of responses over time
- Plot different histograms based upon UTK affiliation
- Explore the content of text