---
title: "Analyze Form Responses"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
```

# Loading packages and reading data

First, we'll load two packages that we will use. These add particular functionality
to R.

```{r}
library(tidyverse)
library(janitor)
library(lubridate)
```

We'll read data from a URL. Note that the data is *anonymized* and was "published" via
Google Sheets:

```{r}
form_data <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vQWUfMMUboX4YMwz97zz_Z-lh2NrBbMbxVOf56LQooDHtdepLh-_-yXKOLOGHNdRmZI2Xn2kUVtstHH/pub?output=csv")
```

# Preparing data

## Renaming variables

Let's rename the variables to be easier to use.

Before that, let's clean them:

```{r}
form_data <- clean_names(form_data)

names(form_data)
```

They are still very long; however, now, we can more easily rename them:

```{r}
form_data <- form_data %>% 
  rename(prior_exp = what_is_the_extent_of_your_prior_experience_using_r_markdown,
         why_interest = why_in_brief_are_you_interested_in_learning_r_markdown_or_r,
         utk_affiliated = are_you_affiliated_with_the_university_of_tennessee_knoxville_as_a_student_or_faculty_staff_member,
         comments = do_you_have_any_other_questions_or_comments)
```

## Modifying variables

One variables need some additional processing to be more useful to us, `timestamp`.

We'll start with `timestamp`, which needs to be recognized as a time:

```{r}
form_data <- form_data %>% 
  mutate(timestamp = mdy_hms(timestamp))
```

Let's check that it worked:

```{r}
form_data
```